Psychological Needs During Intergroup Contact

### 2021-11-08 Methods-and-Results.Rmd
AOT-M Allport vs. Core comparison code added

# Save variances
mdlMedical$varAttNullType <- 
  VarCorr(mdlMedical$lmeAttNullType) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedical$tauAttNullType <- 
  as.numeric(mdlMedical$varAttNullType[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedical$sigmaAttNullType <- 
  as.numeric(mdlMedical$varAttNullType[2])
# The ICC estimate (between/between+within) is:
mdlMedical$IccAttNullType <-
  (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))
mdlMedical$IccPercAttNull <-
  ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100
```
```{r medicalModelInterceptAttType, include = FALSE}
# Create and save Model
mdlMedical$lmeInterceptAttType <-
  lme(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
    random =  ~ 1 | PID,
    na.action=na.omit,
    data = dtMedical$full
  )

@@

# Save variances
mdlMedical$varInterceptAttType <- 
  lme4::VarCorr(mdlMedical$lmeInterceptAttType)
```
```{r medicalModelSlopesInteractionType, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedical$lmeSlopesAttType <- lme(
  AttitudesDutch ~
    OutgroupInteraction + NonOutgroupInteraction,
  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
  control = lmeControl(opt = "optim"),
  na.action = na.omit,
  data = dtMedical$full
)

@@

# Save variances
mdlMedicalOut$Att$varNull <- 
  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Att$tauNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Att$sigmaNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Att$IccNull <-
  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
mdlMedicalOut$Att$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
```
```{r medicalOutModelInterceptAttAllport, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllport <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptAllport <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
```
```{r medicalOutModelSlopesAttAllport, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllport <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Attempts at R^2
r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
                                 mdlMedicalOut$Att$lmerInterceptAllport, 
                                 mdlMedicalOut$Att$lmerSlopesAllport)

@@

# Save variances
mdlMedicalOut$Qlt$varNull <- 
  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Qlt$tauNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Qlt$sigmaNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Qlt$IccNull <-
  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
mdlMedicalOut$Qlt$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
```
```{r medicalOutModelInterceptQltAllport, include=FALSE}
# Create and save Model
mdlMedicalOut$Qlt$lmeInterceptAllport <-
  lme(
    qualityOverall ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Qlt$varInterceptAllport <-
  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptAllport)
```
```{r medicalOutModelSlopesQltAllport, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Qlt$lmeSlopesAllport <-
  lme(
    qualityOverall ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

```
```{r medicalOutModelInterceptAttAllportQlt, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllportQlt <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptAllportQlt <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllportQlt)
```
```{r medicalOutModelSlopesAttAllportQlt, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllportQlt <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

```{r medicalOutModelMLAttNull, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmerNull <-
  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
mdlMedicalOut$Att$lmeNull <-
  lme(
    AttitudesDutch ~ 1,
    random = ~ 1 | PID,
    data = dtMedicalSupp$medicalOutWithinBetween,
    na.action = na.omit,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

# Save variances
mdlMedicalOut$Att$varNull <- 
  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Att$tauNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Att$sigmaNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Att$IccNull <-
  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
mdlMedicalOut$Att$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
```
```{r medicalOutModelInterceptAttCore, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCore <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptCore <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCore)
```
```{r medicalOutModelSlopesAttCore, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesCore <-
  lme(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Qlt$varNull <- 
  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Qlt$tauNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Qlt$sigmaNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Qlt$IccNull <-
  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
mdlMedicalOut$Qlt$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
```
```{r medicalOutModelInterceptQltCore, include=FALSE}
# Create and save Model
mdlMedicalOut$Qlt$lmeInterceptCore <-
  lme(
    qualityOverall ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Qlt$varInterceptCore <-
  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptCore)
```
```{r medicalOutModelSlopesQltCore, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Qlt$lmeSlopesCore <-
  lme(
    qualityOverall ~
      KeyNeedFulfillment_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

```
```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCoreQlt <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptCoreQlt <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreQlt)
```
```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesCoreQlt <-
  lme(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc + qualityOverall_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

>>>>

# Save variances
mdlMedical$varAttNullType <- 
  VarCorr(mdlMedical$lmeAttNullType) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedical$tauAttNullType <- 
  as.numeric(mdlMedical$varAttNullType[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedical$sigmaAttNullType <- 
  as.numeric(mdlMedical$varAttNullType[2])
# The ICC estimate (between/between+within) is:
mdlMedical$IccAttNullType <-
  (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))
mdlMedical$IccPercAttNull <-
  ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100
```

```{r medicalModelInterceptAttType, include = FALSE}
# Create and save Model
mdlMedical$lmeInterceptAttType <-
  lme(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
    random =  ~ 1 | PID,
    na.action=na.omit,
    data = dtMedical$full
  )

@@

# Save variances
mdlMedical$varInterceptAttType <- 
  lme4::VarCorr(mdlMedical$lmeInterceptAttType)
```

```{r medicalModelSlopesInteractionType, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedical$lmeSlopesAttType <- lme(
  AttitudesDutch ~
    OutgroupInteraction + NonOutgroupInteraction,
  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
  control = lmeControl(opt = "optim"),
  na.action = na.omit,
  data = dtMedical$full
)

@@

# Save variances
mdlMedicalOut$Att$varNull <- 
  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Att$tauNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Att$sigmaNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Att$IccNull <-
  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
mdlMedicalOut$Att$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
```

```{r medicalOutModelInterceptAttAllport, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllport <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptAllport <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
```

```{r medicalOutModelSlopesAttAllport, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllport <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Attempts at R^2
#r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
                                 mdlMedicalOut$Att$lmerInterceptAllport, 
                                 mdlMedicalOut$Att$lmerSlopesAllport)

@@

# Save variances
mdlMedicalOut$Qlt$varNull <- 
  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Qlt$tauNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Qlt$sigmaNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Qlt$IccNull <-
  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
mdlMedicalOut$Qlt$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
```

```{r medicalOutModelInterceptQltAllport, include=FALSE}
# Create and save Model
mdlMedicalOut$Qlt$lmeInterceptAllport <-
  lme(
    qualityOverall ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Qlt$varInterceptAllport <-
  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptAllport)
```

```{r medicalOutModelSlopesQltAllport, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Qlt$lmeSlopesAllport <-
  lme(
    qualityOverall ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

```{r medicalOutModelInterceptAttAllportQlt, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllportQlt <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptAllportQlt <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllportQlt)
```

```{r medicalOutModelSlopesAttAllportQlt, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllportQlt <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

<!-- ```{r medicalOutModelMLAttNull, include=FALSE} -->
<!-- # Create and save Model -->
<!-- mdlMedicalOut$Att$lmerNull <- -->
<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
<!-- mdlMedicalOut$Att$lmeNull <- -->
<!--   lme( -->
<!--     AttitudesDutch ~ 1, -->
<!--     random = ~ 1 | PID, -->
<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
<!--     na.action = na.omit, -->
<!--     control = list(opt = "nlmimb") -->
<!--   ) # use optim if it does not converge -->

<!-- # Get summary with p-values (Satterthwaite's method) -->
<!-- # summary(Null.Out.ML.r) #or with the lme function -->
<!-- summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE) -->

<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full), -->
<!-- #                  method="boot",nsim=1000, -->
<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
<!-- #          "output/tables/ML-Null-CI.csv") -->

<!-- # Save variances -->
<!-- mdlMedicalOut$Att$varNull <-  -->
<!--   VarCorr(mdlMedicalOut$Att$lmeNull) # save variances -->
<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
<!-- mdlMedicalOut$Att$tauNull <-  -->
<!--   as.numeric(mdlMedicalOut$Att$varNull[1]) -->
<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
<!-- mdlMedicalOut$Att$sigmaNull <-  -->
<!--   as.numeric(mdlMedicalOut$Att$varNull[2]) -->
<!-- # The ICC estimate (between/between+within) is: -->
<!-- mdlMedicalOut$Att$IccNull <- -->
<!--   (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2]))) -->
<!-- mdlMedicalOut$Att$IccPercNull <- -->
<!--   ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100 -->
<!-- ``` -->
```{r medicalOutModelInterceptAttCore, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCore <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptCore <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCore)
```

```{r medicalOutModelSlopesAttCore, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesCore <-
  lme(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

<!-- ```{r medicalOutModelMLQltNull, include=FALSE} -->
<!-- # Create and save Model -->
<!-- mdlMedicalOut$Qlt$lmerNull <- -->
<!--   lme4::lmer(qualityOverall ~ 1 + (1 | PID),  -->
<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
<!-- mdlMedicalOut$Qlt$lmeNull <- -->
<!--   mdlMedicalOut$Qlt$lmeNull <-lme( -->
<!--     qualityOverall ~ 1, -->
<!--     random = ~ 1 | PID, -->
<!--     na.action = na.omit, -->
<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
<!--     control = list(opt = "nlmimb") -->
<!--   ) # use optim if it does not converge -->

<!-- # Get summary with p-values (Satterthwaite's method) -->
<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
<!-- summ(mdlMedicalOut$Qlt$lmerNull, digits = 3) -->

<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction), -->
<!-- #                  method="boot",nsim=1000, -->
<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
<!-- #          "output/tables/ML-Null-CI.csv") -->

<!-- # Save variances -->
<!-- mdlMedicalOut$Qlt$varNull <-  -->
<!--   VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances -->
<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
<!-- mdlMedicalOut$Qlt$tauNull <-  -->
<!--   as.numeric(mdlMedicalOut$Qlt$varNull[1]) -->
<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
<!-- mdlMedicalOut$Qlt$sigmaNull <-  -->
<!--   as.numeric(mdlMedicalOut$Qlt$varNull[2]) -->
<!-- # The ICC estimate (between/between+within) is: -->
<!-- mdlMedicalOut$Qlt$IccNull <- -->
<!--   (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2]))) -->
<!-- mdlMedicalOut$Qlt$IccPercNull <- -->
<!--   ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100 -->
<!-- ``` -->

```{r medicalOutModelInterceptQltCore, include=FALSE}
# Create and save Model
mdlMedicalOut$Qlt$lmeInterceptCore <-
  lme(
    qualityOverall ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Qlt$varInterceptCore <-
  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptCore)
```

```{r medicalOutModelSlopesQltCore, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Qlt$lmeSlopesCore <-
  lme(
    qualityOverall ~
      KeyNeedFulfillment_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCoreQlt <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

# Save variances
mdlMedicalOut$Att$varInterceptCoreQlt <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreQlt)
```

```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesCoreQlt <-
  lme(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc + qualityOverall_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

@@

```{r AllportVsCore, include=FALSE}

# Compare new model to previous step
anova(mdlMedicalOut$Att$lmeSlopesAllport, 
      mdlMedicalOut$Att$lmeSlopesCore) %>%
  as.data.frame() %>%
  select(-call) %>%
  kbl(
    .,
    caption = "Medical: Comparison of Allport's Conditions to Core Situational Need",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

AIC(

)

performance::compare_performance(
  mdlMedicalOut$Att$lmerSlopesAllport,
  mdlMedicalOut$Att$lmerSlopesCore
)
```

```{r medicalOutModelInterceptAttCoreAllport, include=FALSE}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCoreAllport <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptCoreAllport <-
    lmer(
      AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3
)

mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
  confint(mdlMedicalOut$Att$lmerInterceptCoreAllport)

# Compare new model to previous step
anova(
  mdlMedicalOut$Att$lmeNull, 
  mdlMedicalOut$Att$lmeInterceptAllport,
  mdlMedicalOut$Att$lmeInterceptCoreAllport
  ) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Medical: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedicalOut$Att$varInterceptCoreAllport <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreAllport)
```

```{r medicalOutModelSlopesAttCoreAllport, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesCoreAllport <-
  lme(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc + AllportsCondition_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesCoreAllport <- lmer(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc + AllportsCondition_cwc +
      (1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3
)

mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
  confint(mdlMedicalOut$Att$lmerSlopesCoreAllport, method = "Wald")

# Compare new model to previous step
anova(
  mdlMedicalOut$Att$lmeNull,
  mdlMedicalOut$Att$lmeInterceptCoreAllport,
  mdlMedicalOut$Att$lmeSlopesCoreAllport
) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Medical: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedicalOut$Att$varSlopesCoreAllport <- 
  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreAllport)

# Assumption Checks:
mdlMedicalOut$Att$diagSlopesCoreAllport <- 
  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreAllport, type = "diag")
grid.arrange(
  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
)

# Plot prediction model
mdlMedicalOut$Att$predSlopesCoreAllport <- 
  dtMedicalSupp$medicalOutWithinBetween %>% 
  filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreAllport,
                           dtMedicalSupp$medicalOutWithinBetween %>% 
                             filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
                           re.form = NA
                           )
         )
